---
title: "EFSA Submission v1"
subtitle: "Data export of trace elements for EFSA submission"
---

```{css, echo=FALSE}
th {
  white-space: nowrap;
}
```

The page presents the data export of trace elements in background sediments from the pilot database. Source tables and columns refer to the [DB Schema](db-schema.qmd) of this project.

::: {.callout-note}
The location columns this mapping draws on (`dist_to_coast`, the nearest country and
its code, `municipality`, `sea_name`) are **reserved but empty** in the pilot
database. The mapping below is the schema mapping, not a statement about coverage:
the values are derived at the clean stage, which recomputes and overwrites them. See
[DB Schema](./db-schema.qmd).
:::

```{r}
library(dplyr)
library(tibble)

efsa_submission <- tribble(
  ~Column,            ~`Lookup`, ~Optionality, ~Table,             ~`Column Names`,                        ~`Fixed Text`,      ~Missing,
  "sampleId",         NA,        "Mandatory",  "sample",           "sample_id",                            NA,                 NA,
  "recId",            "Yes",     "Mandatory",  NA,                 NA,                                     NA,                 NA,
  "envComp",          NA,        "Mandatory",  NA,                 NA,                                     "marine sediment",  NA,
  "pristineLoc",      NA,        "Mandatory",  NA,                 NA,                                     "Yes",              NA,
  "sampleLocGC",      NA,        "Mandatory",  "site",             "latitude + longitude",                 NA,                 NA,
  "sampleLocCM",      NA,        "Mandatory",  "site",             "country + municipality",                NA,                 NA,
  "sampleDate",       NA,        "Mandatory",  "sample",           "date",                                 NA,                 NA,
  "traceElText",      NA,        "Mandatory",  "parameter",        "param_description",                    NA,                 NA,
  "traceElCode",      "Yes",     "Mandatory",  NA,                 NA,                                     NA,                 NA,
  "specText",         NA,        "Mandatory",  "parameter",        'param_description + " (Total)"',       NA,                 NA,
  "specCode",         "Yes",     "Mandatory",  NA,                 NA,                                     NA,                 NA,
  "conc",             NA,        "Mandatory",  "sediment",         "value",                                NA,                 NA,
  "unitText",         NA,        "Mandatory",  "sediment",         "unit",                                 NA,                 NA,
  "unitCode",         "Yes",     "Mandatory",  NA,                 NA,                                     NA,                 NA,
  "weightText",       NA,        "Mandatory",  "sediment",         "basis",                                NA,                 NA,
  "weightCode",       "Yes",     "Mandatory",  NA,                 NA,                                     NA,                 NA,
  "methAnText",       NA,        "Mandatory",  "analysis_method",  "metoa",                                NA,                 NA,
  "methAnCode",       "Yes",     "Mandatory",  NA,                 NA,                                     NA,                 NA,
  "LOD",              NA,        "Optional",   "lld",              "lod",                                  NA,                 NA,
  "LOQ",              NA,        "Optional",   "lld",              "loq",                                  NA,                 NA,
  "accLab",           NA,        "Optional",   NA,                 NA,                                     "No",               NA,
  "phSed",            NA,        "Optional",   NA,                 NA,                                     NA,                 "Yes",
  "TextureSedClay",   NA,        "Optional",   "sediment",         "value (grain-size param, see Sediment Fractions page)", NA, NA,
  "TextureSedSilt",   NA,        "Optional",   "sediment",         "value (grain-size param, see Sediment Fractions page)", NA, NA,
  "TextureSedSand",   NA,        "Optional",   "sediment",         "value (grain-size param, see Sediment Fractions page)", NA, NA,
  "unitText2",        NA,        "Optional",   NA,                 NA,                                     "%",                NA,
  "unitCode2",        "Yes",     "Optional",   NA,                 NA,                                     NA,                 NA,
  "weightText2",      "Yes",     "Optional",   NA,                 NA,                                     NA,                 NA,
  "weightCode2",      "Yes",     "Optional",   NA,                 NA,                                     NA,                 NA,
  "ocSed",            NA,        "Optional",   "sediment",         "value (organic-matter param)",         NA,                 NA,
  "unitText3",        NA,        "Optional",   "sediment",         "unit",                                 NA,                 NA,
  "unitCode3",        "Yes",     "Optional",   NA,                 NA,                                     NA,                 NA,
  "weightText3",      "Yes",     "Optional",   NA,                 NA,                                     NA,                 NA,
  "weightCode3",      "Yes",     "Optional",   NA,                 NA,                                     NA,                 NA,
  "phWater",          NA,        "Optional",   NA,                 NA,                                     NA,                 "Yes",
  "hardWater",        NA,        "Optional",   NA,                 NA,                                     NA,                 "Yes",
  "DOC",              NA,        "Optional",   NA,                 NA,                                     NA,                 "Yes",
  "unitText5",        NA,        "Optional",   NA,                 NA,                                     NA,                 NA,
  "unitCode5",        "Yes",     "Optional",   NA,                 NA,                                     NA,                 NA,
  "publicData",       NA,        "Optional",   NA,                 NA,                                     "Yes",              NA,
  "refPublication",   NA,        "Optional",   "reference",        "ref + ref_description",                NA,                 NA,
  "comments",         NA,        "Optional",   NA,                 NA,                                     NA,                 "Yes",
  "Missing recId",        "Yes", "Optional",   NA,                 NA,                                     NA,                 NA,
  "Missing envComp",      "Yes", "Optional",   NA,                 NA,                                     NA,                 NA,
  "Missing pristineLoc",  "Yes", "Optional",   NA,                 NA,                                     NA,                 NA,
  "Missing sampleLoc",    "Yes", "Optional",   NA,                 NA,                                     NA,                 NA,
  "Missing sampleDate",   "Yes", "Optional",   NA,                 NA,                                     NA,                 NA,
  "Missing traceEl",      "Yes", "Optional",   NA,                 NA,                                     NA,                 NA,
  "Missing spec",         "Yes", "Optional",   NA,                 NA,                                     NA,                 NA,
  "Missing conc",         "Yes", "Optional",   NA,                 NA,                                     NA,                 NA,
  "Missing methAn",       "Yes", "Optional",   NA,                 NA,                                     NA,                 NA
)

efsa_submission_full <- efsa_submission %>%
  mutate(
    across(
      where(is.character),
      ~coalesce(.x, "")
    )
  ) %>%
  rename(c(`Source Table` = "Table",
           `Source Columns` = "Column Names"))

efsa_submission <- efsa_submission_full %>%
  filter(Lookup != "Yes") %>%
  dplyr::select(-c(Lookup, Missing))

```

## Data Mapping for Submission
```{r}
efsa_submission
```

## Full Data Mapping
```{r}
efsa_submission_full
```

## Data Export Method
As the EFSA submission tool is an Excel file containing embedded macros, the data must be mapped column by column rather than through a standard row‑based export. This approach ensures that the structure of the submission file is not disrupted.
